Flabby and injective objects in toposes

### 2018-10-18 paper-flabby-objects.tex
Beginning of section on internalizing higher direct images

\section{Characterizing cohomology}

XXX
% EXT, TOR
% Higher direct images

>>>>

\section{Higher direct images as internal sheaf cohomology}

Let~$X$ be a locale and let~$f : Y \to X$ be an over-locale. By the fundamental
relation between locales and topological spaces, this situation arises
for instance, when given a sober topological space and a topological
space over it, as is often the case in algebraic topology or algebraic
geometry. Let a sheaf~$\O_Y$ of rings on~$Y$ be given. Then the
traditional way to define the \emph{higher direct images} of a sheaf~$E$
of~$\O_Y$-modules is to pick an injective resolution~$0 \to E \to I^\bullet$
and set~$R^n f_*(E) \defeq H^n(\Gamma(I^\bullet))$.

We adopt in this section the axiom of choice, so that enough injectives are
available to ensure that this recipe can be carried out. The resulting sheaf
of~$f_*\O_Y$-modules is well-defined in the following sense: Given a further
injective resolution~$0 \to E \to J^\bullet$, there is up to homotopy precisely
one morphism~$I^\bullet \to J^\bullet$ compatible with the identity on~$E$, and
this morphism induces an isomorphism on cohomology.

Higher direct images are pictured as a ``relative'' version of sheaf
cohomology. Due to the result that injectivity of sheaves of modules can be
characterized in the internal language, we can give the following precise
rendering of this slogan.

The over-locale~$Y$ corresponds to a locale~$I(Y)$ internal to~$\Sh(X)$, in
such a way that the category of internal sheaves over this internal locale
coincides with~$\Sh(Y)$~\cite{XXX}; in particular, a given sheaf~$E$ of~$\O_Y$-modules can
be regarded as a sheaf over~$I(Y)$. Under this equivalence, the morphism~$f : Y
\to X$ corresponds to the unique morphism~$I(Y) \to \mathrm{pt}$ to the
internal one-point locale. Hence it makes sense to construct, from the internal
point of view of~$\Sh(X)$, the sheaf cohomology~$H^n(I(Y), E)$ of~$E$.

\begin{thm}The sheaf on~$X$ obtained by evaluating the expression~``$H^n(I(Y),
E)$'' of the internal language of~$\Sh(X)$ coincides with~$R^n
f_*(E)$.\end{thm}

\begin{proof}We recall that the stack semantics is idempotent in the sense
that~$\Sh(X) \models (\Sh(I(Y)) \models \varphi)$ if and only if~$\Sh(Y)
\models \varphi$. Hence a sheaf of modules on~$Y$ is injective if and only if
it is an injective module from the point of view of~$\Sh(Y)$, if and only if it
is ... XXX Since we have assumed the axiom of choice in the metatheory and
since internal and external injectivity coincide by
Theorem~\ref{thm:injectivity-external-internal}, the statement~``any module has
an injective resolution'' holds internally to~$\Sh(Y)$. Therefore the
statement XXX
\end{proof}
